Panel Seminars

### 2023-02-13 contributions.Rmd
publishing submissions_instructions page to website and pushing some other cache files

---
title: "Contributors"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Original Working Group Members

>>>>

---
title: "Contributions"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# How to contribute new material to the website
If you are interested in submitting new content to the
MarineOmics.github.io website, we have a [guide](submissions_instructions.html) for you!
While the website managers will work with you to help prepare and publish your new
page, this guide can be a useful resource as you develop your content. The guide provides general instructions as well as examples of how to build specific features (eg., tables, code chunks). Prior to developing new pages, please contact the current Website Manager Jason Johns (jasonjohns[at]ucsb.edu). Do not hesitate to reach out with any other questions, comments, or features you'd like added to the guide.

# Original working group members

### 2023-02-13 index.Rmd
publishing submissions_instructions page to website and pushing some other cache files

>>>>

# Making contributions to the MarineOmics website
We are excited to incorporate new material from contributors of various backgrounds, expertise, and experience. To date these tutorials, guidelines,  and discussions have been authored and led by graduate students and postdocs with contributions from scientists at all levels, including undergraduates, technicians, and faculty members. A diverse range of perspectives and backgrounds will make these tutorials more inclusive, informative, and useful for everyone in the marine-omics community. If you are interested in developing an information page or tutorial for the website,  we ask that you review our [page with instructions for submitting content](submissions_instructions.html) and contact our Website Manager Jason Johns (jasonjohns[at]ucsb.edu).
